%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage{hyperref}

\textheight = 9.75in
\textwidth = 6in

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Pankaj Prateek Kewalramani}
\begin{resume}

  %__________________________________________________________________________________________________________________
  % Contact Information
  \section{\mysidestyle Contact\\Information}

  Dept. of Computer Science and Engineering                            \hfill E-mail: pratikkr@cse.iitk.ac.in  \vspace{0mm}\\\vspace{0mm}%
  Indian Institute of Technology, Kanpur                               \hfill pankaj200292@gmail.com  \vspace{0mm}\\\vspace{0mm}%
  Website: \url{http://cse.iitk.ac.in/users/pratikkr/}                                                                      \hfill Mobile: +91 94 50 039421 \vspace{0mm}\       \vspace{0mm}\\\vspace{-4.5mm}%


  %__________________________________________________________________________________________________________________
  % Research Interests
  %% \section{\mysidestyle Research\\Interests}

  %% \begin{itemize}\itemsep0pt
  %% \item Design and Analysis of Algorithms
  %% \item Approximation Algorithms
  %% \item Competitive Programming
  %% \item Artificial Intelligence, Machine Learning and Natural Language Processing
  %% \item Number Theory and Cryptology
  %% \item Programming Languages
  %% \item Compilers and Compilers Concurrency
  %% \end{itemize}


  %__________________________________________________________________________________________________________________
  % Education
  \section{\mysidestyle Education}

  \textbf{Indian Institute of Technology, Kanpur, India} \vspace{2mm}\\\vspace{1mm}%
  \textsl{B.Tech-M.Tech in Computer Science and Engineering} \hfill \textbf{July 2010 -- present}\vspace{-3mm}\\\vspace{-1mm}%
  \begin{list2}
  \item Cumulative Performance Index (CPI) (M.Tech. curriculum) of \textbf{\textsf{9.3}} (on a scale of 10)
  \item Cumulative Performance Index (CPI) of \textbf{\textsf{8.9}} (on a scale of 10)
  \item Expected graduation date: June 2015
  \end{list2}\vspace{-1.5mm}
  \textbf{DAV Public School, Kota} \vspace{2mm}\\\vspace{1mm}%
  \textsl{All India Senior Secondary Certificate Examination (AISSCE)} \hfill \textbf{July 2008 -- May 2010}\vspace{-3mm}\\\vspace{-1mm}%
  \begin{list2}
  \item Scored \textbf{\textsf{91.0\%}} marks in AISSCE Examination
  \end{list2}
  \textbf{St. Anne's Sr. Sec. School, Jodhpur} \vspace{2mm}\\\vspace{1mm}%
  \textsl{All India Secondary School Examination (AISSE)} \hfill \textbf{July 1996 -- May 2008}\vspace{-3mm}\\\vspace{-1mm}%
  \begin{list2}
  \item Scored \textbf{\textsf {95.0\%}} marks in AISSE Examination
  \end{list2}
  \vspace{-1mm}%


  %__________________________________________________________________________________________________________________
  % Honours and Awards
  \section{\mysidestyle Scholastic Achievements}
  \begin{itemize}
  \item Secured \textbf{\textsf{All India Rank 157}} (among 4,00,000 students) in IIT-JEE 2010.
  \item Secured \textbf{\textsf{All India rank 160}} (among 11,00,000 students) in AIEEE 2010.
  \end{itemize}

  \section{\mysidestyle Internships}
  \begin{itemize}
  \item \large{\textbf{\textsf{``Hunting Compiler Concurrency bugs using x86-tso memory model''}}}
    \\ \small{\textit{Summer Internship at INRIA, under Prof. Francesco Zappa Nardelli (May '13- July '13)}}
    \normalsize
    \begin{itemize}
    \item Worked with team ``parkas'' at INRIA, Paris-Rocquencourt
    \item Worked on the Intel x86 instrumentation and tracing in the ``cmmtest'' tool. 
    \item The cmmtest tool performs random testing of C and C++ compilers against the C11/C++11 memory model. A test case is any well-defined, sequential C program; for each test case, cmmtest:
      \begin{enumerate}
      \item compiles the program using the compiler and compiler optimization that are being tested;
      \item runs the compiled program in an instrumented execution environment that logs all memory accesses to global variables and synchronisations;
      \item compares the recorded trace with a reference trace for the same program, checking if the recorded trace can be obtained from the reference trace by valid eliminations, reorderings and introductions.
      \end{enumerate}
      \item Modified the code so that the stack accesses are ignored from the memory trace instrumentation, thus considering only the global trace.
      \item Modified the model to ignore stack traces.
      \item Added support in the tool for the 128-bit mmx/sse instructions. MMX/SSE2 is a single instruction, multiple data (SIMD) instruction set designed by Intel.
      \item Added support for the control dependency analysis of instructions. (If the load of a variable affects a later load of some other variable via a compare (if-then-else) or a jump instruction (loops etc.), then the latter load is control dependent on the second). Control dependency information can be used to test whether the compiler preserve dependence among the variables and to refine the release-acquire semantics.
      \item Modified the replay instrumentation to instrument locks/unlocks, mutex variables and threads and merged it with the existing tool (Replay instrumentation essentially modifies the value of a global load and then instruments the program. If the modified value of the load affects the value of some write then the load is relevant else it is irrelevant to the program).
      \item Added replay instrumentation, support for control dependency analysis and mmx/sse instructions to ``cmmtest'' tool.
      \item The details of the project are available at \url{https://raweb.inria.fr/rapportsactivite/RA2013/parkas/uid30.html}
    \end{itemize}
  \end{itemize}
  %__________________________________________________________________________________________________________________
  \section{\mysidestyle Projects Undertaken}

  \begin{itemize}
  \item \large{\textbf{\textsf{``Handling Anaphora in Multiple Languages for Geometry Construction contexts''}}}
    \\ \small{\textit{B.tech Project under Prof. Amitabha Mukerjee (IIT Kanpur), Dr. Sumit Gulwani (Microsoft Research, Redmond) \& Prof. Amey Karkare (IIT Kanpur) (July 2013 - now)}}
    \normalsize
    \begin{itemize}
    \item Designed a language-independent expert system that processes domain-specific geometry construction problems posed from the middle school textbooks
    \item Developed a parallel corpus for geometry constructions in English and Hindi using NCERT textbooks
    \item The project involved natural language processing of the posed question, mapping the natural language input from the users to solve a construction problem, via cross-lingual mapping and heuristic parsing, to a set of construction steps which were used to generate the intended construction
    \item Defined a task context based semantic analysis system to handle anaphora
    \item Designed a language-independent system for geometry construction problems using cross-lingual mapping, heuristic based parsing and context based semantic analysis
    \item The corpus, code and report are available at \url{http://cse.iitk.ac.in/users/pratikkr/btp/index.html}
    %\item Attempts to tutor the user by posing problems on specified concepts and of graded difficulty
    \end{itemize}

  \item \large{\textbf{\textsf{``Parser Generator in Python''}}}
    \\ \small{\textit{Mentor: Dr. Amey Karkare, CSE, IITK (May '12 - July '12)}}
    \normalsize
    \begin{itemize}
      \item Built a parser generator in Python which takes a BNF form grammar file and performs lexical analysis on it.
      \item To generate the set of rules and determine if the set is valid or not
      \item Compute the first set, follow set, LL(1) Parse Table, LR(0) Item Sets and Parse Table, SLR(1) Parse Table, LR(1) Item Sets and Parse Table and LALR(1) Item Sets and Parse Table of the given grammar file.
      \item Generated a parser to parser grammar expressions using the above.
      \item Designed the GUI using PHP and hosted the working model on the CSE local server. 
      \item Built a parser generator which performs lexical analysis on a BNF grammar and generates the corresponding parser
      \item Internal Link: \url{http://www2.cse.iitk.ac.in/karkare/parsegen/}
    \end{itemize}

  \item \large{\textbf{\textsf{``Learning on the tron bot''}}}
    \\ \small{\textit{Summer Project under Programming Club, IIT Kanpur (May '11 - June '11)}}
    \normalsize
    \begin{itemize}
    \item Developed a Tron bot (based on the movie Tron), incorporating in it learning procedures so that it improves its skills as it plays against other AI bots.
    \item Built an interface using Pygame for the tron game.
    \item Built a learning model to learn by playing against human/bots. Used backtracking to adjust the weights on the feedback of the results.
    \item Tried different Backtracking approaches, and picked the best working one.
    \end{itemize}

  \end{itemize}

  \section{\mysidestyle Course Projects}

  \begin{itemize}

  \item \large{\textbf{\textsf{``Easy Cloud Storage''}}}
    \\ \small{\textit{Course Project: Introduction to Software Engineering (Aug '13 - Nov '13)}}
    \normalsize
    \begin{itemize}
    \item Developed an Easy Cloud Storage platform which integrates all existing cloud storage services such as Dropbox, Google Drive, SkyDrive etc. Provided an abstract layer to the user over his cloud accounts so that he can view them all as a single account. The system would take care of dividing the files over the cloud accounts linked.
    \item Built a web interface for authentication of the user, linking the account to other cloud storage and managing files on them.
    \item Used Software Specification Document, Architecture Diagrams and extreme programming model.
    \item Used PHP for server side programming, Twitter Bootstrap for the UI.
    \item Used API's from Dropbox, Skydrive, box.net, Google Drive.
    \item Developed a desktop application for the service with facilities like auto-syncing of files, storing some file at a particular location etc.
    \item Develop a cloud storage platform integrating various cloud services to allow linking of various accounts
    \item The codes and report can be found at \url{https://github.com/pankajprateek/easyCloud}
    \end{itemize}

  \item \large{\textbf{\textsf{``Compilers for a subset of C++ language features''}}}
    \\ \small{\textit{Course Project: Compiler Design (Feb '13 - Apr '13)}}
    \normalsize
    \begin{itemize}
    \item Implemented a working compiler for a subset of C++ language using C++, LEX, YACC. Applied various aspects of compiler design learned in the code.
    \item Built Lexer and error free grammar
    \item Built Parser along with semantic rules for Symbol Table, user 3-Address Code
    \item Translated the 3-Address code into Assembly language for MIPS architecture
    \item Implemented scoping, type-checking, conditionals and loops
    \end{itemize}

  \item \large{\textbf{\textsf{``Multi-lingual word learning for containment situations''}}}
    \\ \small{\textit{Course Project: Introduction to Cognitive Sciences (Mar '13 - Apr '13)}}
    \normalsize
    \begin{itemize}
    \item Extended the work done by Dr. Amitabha Mukherjee and Madan Dabbeeru in their paper ``Using Symbol Emergence to Discover Multi-Lingual Translations in Design''.
    \item Extended the Baby Designer Model presented in the previous paper to the native Hindi language.
    \item Attempted to learn the synonymous words in multiple languages for a given context by learning common grounded semantics for them followed by label association. 
    \item First learned the design concepts from design specifications and then tried to learn the linguistic representations for them in several languages. 
    \item Demonstrated multi-lingual word learning for containment situations based on our peg-in-hole experiment. 
    \item The corpus, code and report are available at \url{http://home.iitk.ac.in/~pratikkr/se367/project/}
    \end{itemize}

  \item \large{\textbf{\textsf{``Automation of Post-Graduate Application System''}}}
    \\ \small{\textit{Course Project: Principles of Database Systems (Jan '13 - Apr, '13)}}
    \normalsize
    \begin{itemize}
    \item Implemented the portal having facilities for creating students profile. The profile would allow the applicant to apply online as compared to the existing system. The profiles have to be approved by an administrator.         
    \item The interface programming was done in Html and JavaScript, database built on MySql and the interaction between them was done by PHP.
    \end{itemize}

  \item \large{\textbf{\textsf{``Using Progressive Stochastic Search to solve Sudoku Constraint Satisfaction Problem''}}}
    \\ \small{\textit{Course Project: Artificial Intelligence Programming (Jan '12 - Apr '12)}}
    \normalsize
    \begin{itemize}
    \item Modelled Sudoku as a Constraint Satisfaction Problem
    \item Implemented the Progressive Stochastic Search and Iterative Progressive Stochastic Search algo. described in the 2003 IEEE paper ``Using PSS for solving CSPs''
    \item The related codes and documentation can be fetched from \url{http://home.iitk.ac.in/~pratikkr/cs365/projects/}
    \item  Observed that PSS and IPSS are better than other stochastic algorithms viz. Cultural Genetic Algorithm, Quantum Simulated Annealing, Repulsive Particle Swarm Optimization and Hybrid Genetic Algorithm with Simulated Annealing; Used C++
    \end{itemize}

  \item \large{\textbf{\textsf{``Implementation of Internet Protocol Security over a chat client''}}}
    \\ \small{\textit{Course Project: Computer Networks (Sept '12 - Nov '12)}}
    \normalsize
    \begin{itemize}
    \item Implemented Secure IP protocols to send data packets across the network.
    \item Used Diffie-Hellman key exchange algorithm, AES encryption algorithm and authentication headers using md5 hashing
    \item Implemented Diffie-Hellman key exchange algorithm and AES encryption algorithm for the same
    \item Implemented a graphical interface to establish peer to peer connection, send and receive data
    \end{itemize}

  \item \large{\textbf{\textsf{``Extension of the Pintos Operation System''}}}
    \\ \small{\textit{Course project: Operating Systems (Sept '12 - Nov '12)}}
    \normalsize
    \begin{itemize}
    \item Worked on the pintos operating system to add features such as System Calls, shared memory between different programs, solution to the Readers-Writers problem.
    \item Implemented virtual memory with pure demand paging.
    \item Extended the pintos file-system to include sub-directories, implemented a indexed file system supporting direct, indirect and doubly indirect blocks.
    \item Added caching in the buffer during read/write operations.
    \item Includes implementation of techniques for synchronization, demand paging, scheduling, virtual memory management, page fault and swapping, and simple system calls.
    \item Implemented message queues, threads, processes, multiprogramming, scheduling policies, virtual and shared memory management and file-system
    \item Complied with POSIX standards; Implemented and studied various scheduling policies viz. FCFS, SJF, RR; Used C
    \end{itemize}

  \item \large{\textbf{\textsf{``Implementation of MIPS processor on FPGA unit''}}}
    \\ \small{\textit{Course Project: Computer Organization and Architecture (Aug '11 - Oct '11)}}
    \normalsize
    \begin{itemize}
    \item Used Bluespec Verilog(BSV) to implement a simple processor on FPGA.
    \item Built the Arithmetic and Logical Unit (ALU) and a register file of 32 4-bit registers. The input and output were carried out on FPGA using buttons and 7-segment display.  
    \item Programmed a 32-bit ALU on a XILINX Spartan3 FPGA board, using BSV as hardware programming language.
    \item Arithmetic and logical operations could be easily done using this system.
    \end{itemize}

  \end{itemize}

  \section{\mysidestyle Miscellaneous Projects}
  \begin{itemize}
  \item \large{\textbf{\textsf{``Online Judge for Programming Contests''}}}
    \\ \small{\textit{Self-Initiative (Dec '12 - present)}}
    \normalsize
    \begin{itemize}
    \item Worked on the open source project, DomJudge to develop a platform for hosting online programming contests.
    \item The platform has been used to host two international contests and several intra college contests at IIT Kanpur.
    \item Leading a team of six students for further development on the project.
    \item Link to the judge: \url{http://www2.cse.iitk.ac.in/judge/public/}
    \end{itemize}

  \item \large{\textbf{\textsf{``Future TV''}}}
    \\ \small{\textit{Microsoft Code.Fun.Do '13 (Mar '13 - 18 hours)}}
    \normalsize
    \begin{itemize}
    \item Built a service on windows platform using C\# which would render personalised results for the latest and most famous videos.
    \item User can also set the genre of the videos he/she is interested in.
    \end{itemize}

  \item \large{\textbf{\textsf{``Easy Sync (Centralized Cloud Storage)''}}}
    \\ \small{\textit{Microsoft Code.Fun.Do '13 (Mar '13 - 18 hours)}}
    \normalsize
    \begin{itemize}
    \item Developed an app on windows platform using C\# and Windows 8 APIs which automatically syncs all of your web hosted data storage accounts like drop box, SkyDrive account and the folders on your computer 
    \item This app helps to efficiently use the data storage space given by different platforms by removing multiple copies of files and folders stored on separate platforms.
    \item The user was provided with an abstract view of his space across various services and he could also arrange the synced files manually.
    \item Developed a proof-of-concept which could inspire furthur work.
    \item Also added with a user friendly GUI to upload or download data from the cloud.
    \item Extended this project from Windows platform to a web service and a desktop app as a part of Software Development course
    \end{itemize}

  \item \large{\textbf{\textsf{``Simulation''}}}
    \\ \small{\textit{Electrovate, Takneek 2010, IIT Kanpur (Sept '10)}}
    \normalsize
    \begin{itemize}
    \item Simulated a counter which would count the number of people in a room. It would add one to the current value when a person enters a room and subtract one in the other case.
    \item This was done using LEDs, Gates, Flip-Flops, etc. that simulated a system.
    \end{itemize}

  \item \large{\textbf{\textsf{``Peer-to-peer messenger''}}}
    \\ \small{\textit{Code-a-thon 2011 under ACA, IIT Kanpur (Feb '11)}}
    \normalsize
    \begin{itemize}
    \item Developed a peer-to-peer messenger for exchanging messages between two computers connected on a LAN network.
    \item Used C for developing the messenger.
    \end{itemize}

  \item \large{\textbf{\textsf{``Q-Analytics''}}}
    \\ \small{\textit{Yahoo Hack U! 2011 (Aug '11)}}
    \normalsize
    \begin{itemize}
    \item Made a portal for online quizzing. Apart from the normal quizzing modules, it would take the question from the quizmaster and grade it for difficulty by searching for the question and the answer throughout the Web.
    \item This was done by integerating Yahoo APIs with PHP and cURL using OAuth.
    \end{itemize}
    
  \end{itemize}


  %______________________________________________________________________________________________________________________
  \section{\mysidestyle Relevant Courses}

  \begin{tabular}{ll}
    %Verify once
    - Computational Geometry* & - Computational Number Theory and Algebra \\
    - Applications of SDP in Complexity & - Special Topics in Data Compression\\
    - Algorithmic Information Theory & - Approximation Algorithms\\
    - Introduction to Software Engineering & - Modern Cryptography \\
    - Algorithms-II &- Compiler Design \\
    - Principals of Database Systems &- Introduction to Cognitive Sciences \\
    - Principles of Programming Languages &- Computer Networks \\
    - Operating Systems &- Theory of Computation \\
    - Introduction to Mathematical Logic &- Artificial Intelligence Programming \\
    - Programming Tools and Techniques &- Discrete Mathematics \\
    - Data Structures and Algorithms & - Introduction to Computer Organization \\
    - Fundamental of Computing & - Introduction to Electronics\\
    - Differential Equations \& Linear Algebra & - Real and Complex Analysis\\
  \end{tabular}\\
  {\small * - Ongoing}


  %__________________________________________________________________________________________________________________
  % Computer Skills
  \section{\mysidestyle Technical \\Skills}

  \begin{itemize}
  \item \textbf{\textsf{Programming Languages}} - Efficient in C++, C, Python
  \item \textbf{\textsf{Other Programming Languages}} - Pascal, Assembly Language (MIPS and x86 Architecture), OCaml, PHP, BlueSpec Verilog, MySQL, Oz, Bash Script, Windows Batch Script, Basic, Foxpro
  \item \textbf{\textsf{Other Tools}} - Latex, gdb, Intel PinTool, Gnuplot, Octave, HTML5, HTML, Javascript, CSS, Xilinx ISE, AutoCAD, Lex, Yacc, Matlab, MS Office, Visual Studio, PLY (parsing tool in python)
  \item \textbf{\textsf{Hardware}} - Experience with FPGA Boards, Integerated Circuts
  \item \textbf{\textsf{Text Editor}} - Emacs, Vim
  \item \textbf{\textsf{Version Control}} - Git, Mercurial, Subversion
  \item \textbf{\textsf{Operating Systems}} - Worked on Linux (archlinux, ubuntu), Mac, Windows 7/8
  \end{itemize}

  %__________________________________________________________________________________________________________________
  % Computer Skills
  \section{\mysidestyle Positions of Responsibility}

  \begin{itemize}

  \item \textbf{\textsf{Coordinator, ACA (Association of Computing Activities)}}
    \begin{itemize}
      \item Mentored 3 first year students on their assigned projects given through ACA in 2012-13 to complete a project on implementation of the game Tron using Machine Learning
      \item Organized Yahoo! Hack U - a 24 hour coding marathon at IIT-K for the last 2 years in coordination with Yahoo. Received token of appreciation from Yahoo! on organising such a big event.
      \item Organized Code.Fun.Do, a 24-hour Windows App Development contest by Microsoft in 2013 and 2014.
      \item Provided semester long projects in CS field to over 50 first year students through ACA in 2012-13.
      \item Deployed an online judge (\url{http://www2.cse.iitk.ac.in:81/newonj/problem.php}) for practice of programming assignments for students for last 4 semesters with more than 750 registrants. Students from other institutes (IITB, IITR, IIITH and many more) also registered and participating.
      \item Established an online judge for algorithmic contests for 24 hour practice for ACM-ICPC and weekend contests
      \item Mentored a lecture series and training camp for ACM-ICPC for IITK students in 2012 with more than 150 students enrolled.
      \item Organised Fresher’s party for the incoming batch and Farewell for the graduating batch
    \end{itemize}
   
  \item \textbf{\textsf{Instructor, ACA Summer School (June '14)}}
    \begin{itemize}
      \item Taught a course on Advanced C++ as a part of the ACA Summer School with an enrollment of more than 150 students
      \item Topics included discussion on classes, inheritance, polymorhism, STL, templates and exceptions
      \item Course material can be accessed at \url{http://www.cse.iitk.ac.in/users/aca/sumschool2014/lectures.html}
    \end{itemize}

  \item  \textbf{\textsf{Coordinator, IOPC (International Online Programming Contest), Techkriti'13 August 2012-April 2013}}
    \begin{itemize}
    \item Problem Setter and Tester for IOPC.
    \item Setup the problems for IOPC, the annual 24 hr long programming contest during Techkriti (\url{www.codechef.com/IOPC2013})
    \item Worked with a team of 5 members on creating and testing the problems for the 24 hr long programming contest(\url{www.codechef.com/IOPC2013})
    \item Achieved a 100\% increase in the number of teams that participated. Total number of teams being 793.
    \end{itemize}
    
  \item  \textbf{\textsf Coordinator, Software Corner, Techkriti'13 August 2012-April 2013}
    \begin{itemize}
    \item Software Corner represents all the software related competitions during Techkriti. We conducted 5 such events.
    \item Organized the first International High Performance Computing contest, which was hosted on PARAM Yuva supercomputer in collaboration with Centre for Development of Advanced Computing (CDAC). 
    \item Problem setter for IHPC, Techkriti 2013, Asia’s first High Performance Computing programming competition
    \item Revamped Battlecity by taking the contest Online(12x participation) and getting International contestants.
    \item  Battlecity (an AI design challenge), took the contest online for the first time, got a 12x raise in the number of teams(around 600) participating in the contest.
    \item Chaos (an Unknown language programming contest), took the contest to international level and successfully managed to conduct the contests on servers from CSE department of IITK for the first time.
    \item Also conducted two onsite events Hack-a-thon and Instant (Puzzle solving and fast coding competition)
    \item Elevated three contests to international level for the first time.
    \end{itemize}

  \item \textbf{\textsf{Problem setter for Intra IITK Programming Events}}
    \begin{itemize}
    \item Organized and developed problems for many Intra IITK programming contests with more than 300 participants
    \item Lead problem setter for weekend programming contests organized by ACA and Programming Club at IITK
    \end{itemize}

  \item \textbf{\textsf Worked as a Student Guide in the Institute Counselling Service Team 2011-2012}
    \begin{itemize}
    \item Selected through faculty interview to provide counsel and mentor 6 first year students for the term 2010-11
    \item Coordinated with a faculty-guardian to guide students and prevent ragging
    \item Helped and supervised new students during their stay in First Year.
    \item Regular meetings with them to help them adjust to the work culture of IIT Kanpur.
    \end{itemize}

  \item \textbf{\textsf Academic Mentor for the course Physics-I (Mechanics)}
    \begin{itemize}
    \item Planned and took lectures and doubt clearing sessions at hostel as well as institute level to help the students understand the fundamentals of Physics-1
    \item Mentored the students and provided them with academic assistance.
    \item Was given responsibility of two students, who were not doing well in their academics, to help them with academics and in helping them to adjust with the IIT Kanpur work culture.
    \end{itemize}
    
  %% \item \textbf{\textsf Mentored a group of 3 people to build a Intelligent twentynine card game player}
  %%   \begin{itemize}
  %%   \item Guided the group towards reading resources related to the project.
  %%   \item Provided them with constructive feedback and ideas on how to build the player
  %%   \end{itemize}

  \end{itemize}

  
  \section{\mysidestyle Other Activities}
  
  \begin{itemize}
    
  \item  \textbf{\textsf Competitive Programming}
    \begin{itemize}
    \item Won $5^{th}$ prize in Battlecity in Techkriti in 2012.
    \item An active participant of programming events in the college, was first among freshers (overall third) in the Semester Programming Contest in first year, won 1st prize in a coding contest(Kodefest) and $2^{nd}$ prize in Blackbox (puzzles and coding contest) in Takneek 2011, an inter-hostel technical event.
    \item Programming Profiles:       
      \begin{itemize}
      \item Codechef - profile: \href{http://codechef.com/users/boygenius}{boygenius} - long contest rating 1577 %short contest rating 82 - long contest rating 1268 in India.
      \item SPOJ - profile: \href{http://spoj.com/users/pankaj\_prateek}{pankaj\_prateek} - global rank 1007
      \item Division 2 in Codeforces - profile - \href{http://codeforces.com/profile/boygenius}{boygenius} - rating 1550% - India rank 99.
      %% \item Division 1 in \href{http://community.topcoder.com/tc?module=MemberProfile&cr=23043775}{Topcoder} - rating 1215 - India rank 222
      \end{itemize}
    \item Ranked 20 (handle: boygenius) in the Inter-IIT Programming Contest, Interview Street : Rank List: \url{https://iitvsiit.interviewstreet.com/challenges/dashboard/#leaderboard}
    \end{itemize}
  \item Participated in the Yahoo! HackU 2011, Microsoft Appfest 2013 and Microsoft code.fun.do 2013
  \item Attended Certified Information Security Specialist Workshop conducted by CyberCure Solutions at IIT Kanpur in 2011

  \end{itemize}

  \section{\mysidestyle Achievements}
  \begin{itemize}
  \item Selected for Summer Research Fellowship at Carnegie Mellon University.
  \item Interned at Institut national de recherche en informatique et en automatique (INRIA), France.
  \item Secured All India Rank of 157 in JEE-2010 competing against 450,000 applicants
  \item Was among top 0.2\% in All India Engineering Enterance Exam, 2010 conducted by CBSE (AIR-160)
  \item Awarded Gold Medal in the Orientation-cum-Selection Camp (OCSC) for the International Chemistry Olympiad conducted by HBCSE, TIFR in the year 2010 for being in the top 36 candidates at the NPEC-INChO Examination in 2010 out of 28150 candidates
  \item Won $5^{th}$ prize in Battlecity in Techkriti in 2012
  \item Qualified for Indian National Olympiad in Informatics (INOI) in 2008
  \item Awarded the prestigious Kishore Vigyan Protsahan Yojana(KVPY) fellowship by the Department of Science and Technology, Government of India in the year 2008
  \item Awarded the National Talent Search Examination(NTSE) Scholarship from 2008 onwards (Merit List - 24)
  \item Awarded Gold Medal for securing $9^{th}$ position in State Talent Search Examination(SSTSE) organized by the Government of Rajasthan in the year 2008
  \item Secured $1^{st}$ position in the Zonal Level Science Quiz organized by Government of Rajasthan in 2008
  \item Selected amongst the top 1\% students enrolled in the state for the National Standard Examnation in Astronomy in the year 2009
  \item Secured Olympiad rank 7 (state rank 2) in the International Olympiad of Mathematics 2009 organized by the Mathematics Olympiad Foundation
  \item Secured rank 131 in the International Mathematics Olympiad conducted by the Science Olympiad Foundation in 2009
  \item Secured $2^{nd}$ position in the national-level Map Quiz conducted by the Indian National Cartographic Association in 2007
  \item Awarded $2^{nd}$ rank in the Mathematical Genius Award organized by Srijan Foundation in 2007
  \item Won the Siddharth Bhandari Memorial Inter School Science and Environment Quiz (State Level) in 2007
  \item Secured $2^{nd}$ position in the W.W.F Environment Quiz in 2005
  \end{itemize}

  %______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF


